Modelling BCG vaccination in the UK

### 2019-08-05 rmds/index.Rmd
add dissertation text
updated html thesis stuff

@@

`r if(!knitr:::is_latex_output()) knitr::knit_child("00-abstract.Rmd", quiet=TRUE)`

@@

`r if(!knitr:::is_latex_output()) knitr::knit_child("00-acknowledgements.Rmd", quiet=TRUE)`

>>>>

`r if(!knitr:::is_latex_output()) 'A dissertation submitted to the University of Bristol in accordance with the requirements of the degree of Doctor of Philosophy in the Faculty of Health Sciences.'`

@@

```{r abstract, child = "00-abstract.Rmd", eval = !knitr:::is_latex_output()}
```

@@

```{r acknowledgements, child = "00-acknowledgements.Rmd", eval = !knitr:::is_latex_output()}
```
